Wissenschaftliches Arbeiten

### 2014-06-29 review-log.tex
Explaining what n is in the context of complete enumeration as solution strategy of comb. auctions
Correcting wrong reference
Answering reference and literature improvements

\section{Clarity}
\subsection{In Kapitel 1.2, letzter Satz geht nicht ganz klar hervor was ``ordinal preference'' bedeutet. (2)}
Extended the example a bit.
\subsection{In the restaurant example in section 1.5 Combinatorial Domains it is not clear at first glance that the author does not use a combinatorial voting system. (3)}
Redefined the example a bit by stripping not needed parts and reworked the text in general.
\subsection{In section 4 Bidding Representations \& Languages I think the part about XOR-bids can benefit from some more explanations. I feel that it would be easier to understand, if the the dummy items would have been explained further. [FLBS99] actually has a better example.}
\subsection{On page five the article says ``Its upper limit is $O(n^n)$.'' without saying what n is. (3)}

\section{References \& Literature}
\subsection{Sometimes only the page numbers are given (without the word `pages'), sometimes it is `pages 1-12' (1)}
\subsection{In Kapitel 1.1 wäre eine Referenz wünschenswert, ansonsten ausreichend Literatur referenziert. (2)}
\subsection{On page six the paper says ``[CELM07] had a look at the American truckload transportation market during the late 1990s and early 2000s.'' I believe the reference is wrong and should be replaced by [CS06]. The bibliography entry ``[CS06]'' is not referenced anywhere in the article. (3)}

>>>>

\section{Clarity}
\subsection{In Kapitel 1.2, letzter Satz geht nicht ganz klar hervor was ``ordinal preference'' bedeutet. (2)}
Extended the example a bit.
\subsection{In the restaurant example in section 1.5 Combinatorial Domains it is not clear at first glance that the author does not use a combinatorial voting system. (3)}
Redefined the example a bit by stripping not needed parts and reworked the text in general.
\subsection{In section 4 Bidding Representations \& Languages I think the part about XOR-bids can benefit from some more explanations. I feel that it would be easier to understand, if the the dummy items would have been explained further. [FLBS99] actually has a better example.}
\subsection{On page five the article says ``Its upper limit is $O(n^n)$.'' without saying what n is. (3)}
Added.

\section{References \& Literature}
\subsection{Sometimes only the page numbers are given (without the word `pages'), sometimes it is `pages 1-12' (1)}
The inconsistency comes from Google Scholar where different BibTex classes (in proceedings, book, article) are used which appears to render differently. I did not change this to stick to Scholar's output, and live with this inconsistency.
\subsection{In Kapitel 1.1 wäre eine Referenz wünschenswert, ansonsten ausreichend Literatur referenziert. (2)}
From my point of view this is widely known and so a reference is not necessary. Alternatively more information can be found in the references used in the following sub sections.
\subsection{On page six the paper says ``[CELM07] had a look at the American truckload transportation market during the late 1990s and early 2000s.'' I believe the reference is wrong and should be replaced by [CS06]. The bibliography entry ``[CS06]'' is not referenced anywhere in the article. (3)}
Corrected.
